Time slice analyses

### 2017-11-01 analyses/02-time-slice-analyses.Rmd
Add " to metric name

## Ages
out1 <- run.all.disparity.strat(morphospace, tree, type = "Age", FADLAD, inc.nodes = TRUE,
                                bootstraps = 100, metric = c(sum, variances), metric.name = sum_var)
readr::write_csv(out1, path = paste0("../outputs/age", "_", slug, ".csv"))

## Epochs
out2 <- run.all.disparity.strat(morphospace, tree, type = "Epoch", FADLAD, inc.nodes = TRUE,
                        bootstraps = 100, metric = c(sum, variances), metric.name = sum_var)
readr::write_csv(out2, path = paste0("../outputs/epoch", "_", slug, ".csv"))
```

@@

for (bins in c(2, 5, 10, 15, 20)){
  output <- run.all.disparity(morphospace, tree, bins, FADLAD, inc.nodes = TRUE,
                              bootstraps = 100, = c(sum, variances), metric.name = sum_var){

>>>>

## Ages
out1 <- run.all.disparity.strat(morphospace, tree, type = "Age", FADLAD, inc.nodes = TRUE,
                                bootstraps = 100, metric = c(sum, variances), metric.name = "sum_var")
readr::write_csv(out1, path = paste0("../outputs/age", "_", slug, ".csv"))

## Epochs
out2 <- run.all.disparity.strat(morphospace, tree, type = "Epoch", FADLAD, inc.nodes = TRUE,
                        bootstraps = 100, metric = c(sum, variances), metric.name = "sum_var")
readr::write_csv(out2, path = paste0("../outputs/epoch", "_", slug, ".csv"))
```

@@

for (bins in c(2, 5, 10, 15, 20)){
  output <- run.all.disparity(morphospace, tree, bins, FADLAD, inc.nodes = TRUE,
                              bootstraps = 100, metric = c(sum, variances), metric.name = "sum_var")
